\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-15 manuscript.Rmd
ICC updated
Personfit Plot Updated

ICC2 <- cowplot::plot_grid(vic.iic2 , agg.iic2,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 600, bg = "white")
```

@@

F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme+ ylim(0,600) + xlim(-4,2)

@@

F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+
  scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F2")+apatheme+ylim(0,600) + xlim(-4,2)

@@

F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F3")+apatheme+ylim(0,600) + xlim(-4,2)

@@

F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F4")+apatheme+ylim(0,600) + xlim(-4,2)

@@

F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme+ylim(0,600) + xlim(-4,2)

@@

```{r perfit, include=F}
personfit <- plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
          labels = "AUTO", label_size = 12,align = "v", ncol =2,
                       label_fontfamily = "Arial",
                     label_fontface = "plain")

>>>>

@@

F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme+ ylim(0,600) + xlim(-4,2)

@@

F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+
  scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F2")+apatheme+ylim(0,600) + xlim(-4,2)

@@

F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F3")+apatheme+ylim(0,600) + xlim(-4,2)

@@

F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics: F4")+apatheme+ylim(0,600) + xlim(-4,2)

@@

F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
  labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme+ylim(0,600) + xlim(-4,2)

@@

```{r perfit, include=F}
personfit <- cowplot::plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
          labels = "AUTO", label_size = 12,align = "v", ncol =2,
                       label_fontfamily = "Arial",
                     label_fontface = "plain")
